Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2018-02-15 inst/examples/20170201-manuscript.Rmd

```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(dplyr)
place <- "Turku"
catalogue = "Fennica"
df = df0

df <- df %>% filter(catalog == catalogue & publication_place == place)

df <- df %>%	
  filter(publication_year >= 1640 & publication_year <= 1828)%>%
        select(publication_decade, publisher, paper)

@@

@@

#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
# Sort by biggest publication decade
#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher

ord <- as.character((npub %>% group_by(publisher) %>% 
                        summarise(decade = median(publication_decade)) %>% 
                        arrange(decade))$publisher)
npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))

>>>>

```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(dplyr)
place <- "Turku"
catalogue <- "Fennica"
df <- df0

df <- df %>% filter(catalog == catalogue & publication_place == place) %>%
             filter(!is.na(publisher))

df <- df %>%	
  filter(publication_year >= 1640 & publication_year <= 1828) %>%
        select(publication_decade, publication_year, publisher, paper)

@@

# Title count per year & publisher	
npub0 <- df %>% group_by(publication_year, publisher) %>% tally() %>% arrange(n)

@@

# Translate
npub0$publisher <- gsub("ja poika", "and son", npub0$publisher)
npub0$publisher <- gsub("J.C. Frenckell and son", "Frenckell, Johan Christopher & Son", npub0$publisher)
npub0$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub0$publisher)
npub0$publisher <- gsub("Johan Christopher Frenckell's widow", "Frenckell, Johan Christopher's widow", npub0$publisher)

# Order by average publication year
ord <- as.character((npub0 %>% group_by(publisher) %>% 
                        summarise(year = mean(publication_year)) %>% 
                        arrange(year))$publisher)
#ord <- ord[c(1:7, 9, 8, 10:11)]	
npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
